Competing Bandits

### 2018-08-12 analysis_code/agents_table.Rmd
more updates

#dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_tournament_raw_results.csv", sep=""))
#dat_3 <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_large_horizon_3_raw.csv", sep=""))
#dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_many_arms_haystack_raw.csv", sep=""))
#dat_2 <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_many_arms_2_raw.csv", sep=""))
#dat_10 <- rbind(dat, dat_2)
dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_ws_small_erase_rep_raw.csv", sep=""))
dat_3 <- dat

p1_algs <- as.list(unique(dat_3['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat_3['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat_3['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat_3['Time.Horizon']))$Time.Horizon
time_horizons <- c(5000)
priors <- as.list(unique(dat_3['Prior']))$Prior
warm_starts <-  sort(as.list(unique(dat_3['Warm.Start']))$Warm.Start, decreasing=FALSE)

@@

      agent_alg <- agent_algs[i]
      time <- time_horizons[j]
      for (k in 1:length(alg_pairs)) {
        if (k %% 2 == 0) { next }
          p1alg = alg_pairs[k]
          p2alg = alg_pairs[k+1]
          K <- 10
          if (q == 1) {
            filtered_dat <- filter(dat, P1.Alg == p1alg & Warm.Start == start & P2.Alg == p2alg & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          } else {
            filtered_dat <- filter(dat_10, P1.Alg == p1alg & Warm.Start == start & P2.Alg == p2alg & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          }
          if (nrow(filtered_dat) == 0) {
            next
          }
          share <- filtered_dat$Market.Share.for.P1
          test <- t.test(share)
          cin <- signif(test$conf.int[2] - mean(share), digits=1)
          shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
          shares_percent <- signif(shares * 100, digits=2)
          cv_high <- qchisq(.975, df=length(share) - 1)
          cv_low <- qchisq(.025, df=length(share) - 1)
          lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=1)
          high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=1)
          results[i, (k+1)/2] <- paste("<b>",signif(mean(share), digits=2), "</b> +/-", cin, "<br>Var:", signif(var(share), digits=2), "<br>Share:", shares_percent, "%")
          }
      }
      tab <-xtable(results, caption=paste("Results for", "t=",time, prior, "Warm Start=", start, "K=", K), row.header='Entrant', col.header='Incumbent')
      print(tab, type="html")
    }
  }
  }
}

>>>>

dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_full_sim_raw.csv", sep=""))

p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(2000)
priors <- as.list(unique(dat['Prior']))$Prior
warm_starts <-  sort(as.list(unique(dat['Warm.Start']))$Warm.Start, decreasing=FALSE)

@@

      agent_alg <- agent_algs[i]
      time <- time_horizons[j]
      for (k in 1:length(alg_pairs)) {
        if (k %% 2 == 0) { next }
          p1alg = alg_pairs[k]
          p2alg = alg_pairs[k+1]
          K <- 10
          if (q == 1) {
            filtered_dat <- filter(dat, P1.Alg == p1alg & Warm.Start == start & P2.Alg == p2alg & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          } else {
            filtered_dat <- filter(dat, P1.Alg == p1alg & Warm.Start == start & P2.Alg == p2alg & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          }
          if (nrow(filtered_dat) == 0) {
            next
          }
          share <- filtered_dat$Market.Share.for.P1
          test <- t.test(share)
          cin <- signif(test$conf.int[2] - mean(share), digits=1)
          shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
          shares_percent <- signif(shares * 100, digits=2)
          cv_high <- qchisq(.975, df=length(share) - 1)
          cv_low <- qchisq(.025, df=length(share) - 1)
          lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=1)
          high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=1)
          results[i, (k+1)/2] <- paste("<b>",signif(mean(share), digits=2), "</b> +/-", cin, "<br>Var:", signif(var(share), digits=2), "<br>Share:", shares_percent, "%")
          }
      }
      tab <-xtable(results, caption=paste("Results for", "t=",time, prior, "Warm Start=", start, "K=", K), row.header='Entrant', col.header='Incumbent')
      print(tab, type="html")
    }
  }
  }
}

### 2018-08-12 analysis_code/tournament_table.Rmd
more updates

dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_testing_prelim_raw.csv", sep=""))
#dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_free_obs_10_arms_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(2000)
priors <- as.list(unique(dat['Prior']))$Prior

>>>>

dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_full_sim_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(2000)
priors <- as.list(unique(dat['Prior']))$Prior

### 2018-08-12 paper/competing_bandits.tex
more updates

\subsection{Bandit Priors}
We study the implications of our model via simulation. For computational tractability we focus our attention on Bernoulli bandits with beta priors. We consider the following bandit ``priors" from which the bandit instances faced in simulation are drawn:
\begin{enumerate}
\item ``HeavyTail": We took the mean rewards to be randomly drawn from Beta($\alpha=0.6,\beta=0.6$). With this distribution it was likely to have arms that were at the extremes (close to 1 and close to 0) but also some of the arms with intermediate value means. [We should rename this prior instance]
\item Needle-in-haystack High - $K-1$ arms with mean 0.50, 1 arm with mean 0.70. 
\end{enumerate}

@@

Run in isolation we expect that the performance of the algorithms (according to cumulative regret) should be \\
 Adaptive Exploration $>=$ Non-adaptive exploration $>=$ Greedy. We verify that, for the chosen algorithms and chosen priors, this is indeed the case (with some caveats, discussed in the next section).

@@

\begin{algorithm}
\caption{Simulation Pseudo-Code}
\begin{algorithmic}[1]
\For{Each prior $p$}
\State Generate true distribution from $p$
\State Generate $T \times K$ realizations for the arms 
	\For{Each agent algorithm $agent alg$}
		\For{Each principal algorithm pair $principalalg1$, $principalalg2$}
			\For{$N$ simulations}
				\State Give principal 2 $X$ free observations (the agents also get these observations)				
				\State Give the agents $k$ observations from each principal (warm start)
				\State Run simulation for $T$ periods
			\EndFor
		\EndFor
	\EndFor
\EndFor
\end{algorithmic}
\label{alg_1}
\end{algorithm}

@@

In this section we present simulation results of the model discussed in Section \ref{S:2} where $X = 0$ so that both firms enter at the same time. We want to understand what algorithms the firms are incentivized to commit to in the competition game but the payoffs associated with each algorithm are too difficult to compete analytically and thus, we begin by simply imposing that the algorithm played by the firm is taken as given and study the consequences of playing them in the competition game. Additionally, for this experiment we present results for the $HardMax$ agent decision rule and postpone discussion of alternative decision rules. Besides keeping track of market share, we also will keep track of the effective end of game in order to better understand what happens in the game.

\begin{definition}
\textit{Effective End of Game (EEOG)} - the last round, $t$ in a simulation where there is a difference between the decision of the agent alive at $t-1$ and the agent alive at $t$ (todo: state this formally using notation of model)
\end{definition}

@@

\begin{table}[ht]
\label{ht_incum}
\centering
\caption{Incumbent Experiment for Heavy Tail}
\begin{tabular}{rlll}
\multicolumn{3}{c}{Incumbent Algorithm} \\
\multirow{3}{*}{\rotatebox{90}{Entrant Algorithm}} \\
\hline
 & TS & DEG &  DG \\ 
 \hline
TS & \makecell{\textbf{ 0.0067 } $\pm$ 0.0092 \\Variance: 0.007 \\ ES: 100 \%} & \makecell{\textbf{ 0.023 } $\pm$ 0.017 \\Variance: 0.02 \\ ES: 99 \%} & \makecell{\textbf{ 0.064 } $\pm$ 0.027 \\Variance: 0.05 \\ ES: 97 \%} \\ 
\hline
  DEG & \makecell{\textbf{ 0.024 } $\pm$ 0.015 \\Variance: 0.02 \\ ES: 98 \%} & \makecell{\textbf{ 0.13 } $\pm$ 0.034 \\Variance: 0.09 \\ ES: 86 \%} & \makecell{\textbf{ 0.14 } $\pm$ 0.036 \\Variance: 0.1 \\ ES: 89 \%} \\ 
\hline   
   DG & \makecell{\textbf{ 0.063 } $\pm$ 0.024 \\Variance: 0.04 \\ ES: 93 \%} & \makecell{\textbf{ 0.19 } $\pm$ 0.041 \\Variance: 0.1 \\ ES: 91 \%} & \makecell{\textbf{ 0.15 } $\pm$ 0.032 \\Variance: 0.08 \\ ES: 77 \%} \\ 
\end{tabular}
\caption*{\tiny{TODO: fix table names and general table alignment. The first line in each cell contains the average market share for the entrant over $N=250$ simulations as well as a 95\% confidence interval. The second line contains the sample variance of the observed market shares and the third line contains the fraction of simulations that ended up with one principal getting $> 90\%$ of the market. Note that smaller values in the table are better for the incumbent. Market shares are calculated as the fraction of users selecting a particular firm \textit{after} the entrant has already entered (i.e. the free rounds to firm 2 do not count towards the share)}}
\end{table}

@@

\section{Conclusion}
\label{S:10}

\pagebreak
\bibliography{refs}

>>>>

\subsection{Bandit Priors}
We study the implications of our model via simulation. For computational tractability we focus our attention on Bernoulli bandit diBernoulli bandits with beta priors. We consider the following bandit ``priors" from which the bandit instances faced in simulation are drawn:
\begin{enumerate}
\item ``HeavyTail": We took the mean rewards to be randomly drawn from Beta($\alpha=0.6,\beta=0.6$). With this distribution it was likely to have arms that were at the extremes (close to 1 and close to 0) but also some of the arms with intermediate value means. [We should rename this prior instance]
\item Needle-in-haystack High - $K-1$ arms with mean 0.50, 1 arm with mean 0.70. 
\end{enumerate}

@@

Run in isolation we expect that the performance of the algorithms (according to cumulative regret) should be \\
 Adaptive Exploration $\geq$ Non-adaptive exploration $\geq$ Greedy. We verify that, for the chosen algorithms and chosen priors, this is indeed the case (with some caveats, discussed in the next section).

@@

\begin{algorithm}
\caption{Simulation Pseudo-Code}
\begin{algorithmic}[1]
\For{Each prior $p$}
	\For{$N$ simulations}
		\State Generate true distribution from $p$
		\State Generate $T \times K$ realizations for the arms 
		\For{Each agent algorithm $agent alg$}
			\For{Each principal algorithm pair $principalalg1$, $principalalg2$}
				\State Give principal 2 $X$ free observations (the agents also get these observations)
				\State Give the agents $k$ observations from each principal (warm start)
				\State Run simulation for $T$ periods
			\EndFor
		\EndFor
	\EndFor
\EndFor
\end{algorithmic}
\label{alg_1}
\end{algorithm}

@@

In this section we present simulation results of the model discussed in Section \ref{S:2} where $X = 0$ so that both firms enter at the same time. We want to understand what algorithms the firms are incentivized to commit to in the competition game but the payoffs associated with each algorithm are too difficult to compute analytically and thus, we begin by simply imposing that the algorithm played by the firm is taken as given and study the consequences of playing them in the competition game. Additionally, for this experiment we present results for the $HardMax$ agent decision rule and postpone discussion of alternative decision rules. Besides keeping track of market share, we also will keep track of the ``effective end of game."

\begin{definition}
\textit{Effective End of Game (EEOG)} - the last round, $t$, in a simulation where there is a difference between the decision of the agent alive at $t-1$ and the agent alive at $t$ (todo: state this formally using notation of model)
\end{definition}

@@

\begin{table}[ht]
\centering
\caption{Incumbent Experiment Heavy Tail X=200} 
\begin{tabular}{rlll}
\multicolumn{3}{c}{Incumbent Algorithm} \\
\multirow{3}{*}{\rotatebox{90}{Entrant Algorithm}} \\
  \hline
 & TS & DEG &  DG \\ 
  \hline
TS & \makecell{\textbf{ 0.0029 } $\pm$ 0.0029 \\Variance: 0.002 \\ ES: 100 \%} & \makecell{\textbf{ 0.11 } $\pm$ 0.019 \\Variance: 0.09 \\ ES: 96 \%} & \makecell{\textbf{ 0.17 } $\pm$ 0.022 \\Variance: 0.1 \\ ES: 95 \%} \\ 
  DEG & \makecell{\textbf{ 0.049 } $\pm$ 0.011 \\Variance: 0.03 \\ ES: 94 \%} & \makecell{\textbf{ 0.24 } $\pm$ 0.022 \\Variance: 0.1 \\ ES: 74 \%} & \makecell{\textbf{ 0.24 } $\pm$ 0.023 \\Variance: 0.1 \\ ES: 79 \%} \\ 
   DG & \makecell{\textbf{ 0.12 } $\pm$ 0.017 \\Variance: 0.08 \\ ES: 87 \%} & \makecell{\textbf{ 0.35 } $\pm$ 0.026 \\Variance: 0.2 \\ ES: 77 \%} & \makecell{\textbf{ 0.29 } $\pm$ 0.023 \\Variance: 0.1 \\ ES: 65 \%} \\ 
   \hline
\end{tabular}
\caption*{\tiny{TODO: fix table names and general table alignment. The first line in each cell contains the average market share for the entrant over $N=250$ simulations as well as a 95\% confidence interval. The second line contains the sample variance of the observed market shares and the third line contains the fraction of simulations that ended up with one principal getting $> 90\%$ of the market. Note that smaller values in the table are better for the incumbent. Market shares are calculated as the fraction of users selecting a particular firm \textit{after} the entrant has already entered (i.e. the free rounds to firm 2 do not count towards the share)}}
\label{ht_incum}
\end{table}

@@

\bibliography{refs}
